---
title: "Main Sample CMRS Factors, 6-18 Parents (N=2252)"
author: "Marissa McClellan"
output:
  pdf_document: 
    toc: true
    toc_depth: 4
    number_sections: true
  html_document: default
editor_options: 
  markdown: 
    wrap: 80
  chunk_output_type: inline
---

# Load data and packages

```{r}
source("00_libraries_v1.R") ## includes needed packages
source("01_data-cleaning_6to11combo_v1.R")  ## loads 6-11 par sample with needed factors
source("01_data-cleaning_12to18combo_v1.R")  ## loads 12-18 par sample with needed factors
```

```{r}
library(esem)
# library(devtools)
# devtools::install_github("MateusPsi/esemComp", build_vignettes = TRUE)
library(esemComp)
```

## Light data cleaning
```{r}
## Pull out CMRS- Younger Sample

cmrs_young <- parent_young %>%
  select(child_sex_main, child_gender_main, child_age_main, cmrsp01:cmrsp21, cmrsp21tot:cmrsp10pomp)
      
  # only contains 21 items
cmrs21_young_items <- parent_young %>%
  select(cmrsp01:cmrsp21)

# omits missing values (used for reliability and EFA)
cmrs21_young_shrunk <- na.omit(cmrs21_young_items)
      
  # only contains 10 items
cmrs10_young_items <- parent_young %>%
  select(cmrsp01, cmrsp02, cmrsp04, cmrsp05, cmrsp08, cmrsp09, cmrsp12, cmrsp13, cmrsp16, cmrsp20)

# omits missing values (used for reliability and EFA)
cmrs10_young_shrunk <- na.omit(cmrs10_young_items)
```

```{r}
## Pull out CMRS- Older Sample

cmrs_old <- parent_old %>%
  select(child_sex_main, child_gender_main, child_age_main, cmrsp01:cmrsp21, cmrsp21tot:cmrsp10pomp)
      
  # only contains 21 items
cmrs21_old_items <- parent_old %>%
  select(cmrsp01:cmrsp21)

# omits missing values (used for reliability and EFA)
cmrs21_old_shrunk <- na.omit(cmrs21_old_items)
      
  # only contains 10 items
cmrs10_old_items <- parent_old %>%
  select(cmrsp01, cmrsp02, cmrsp04, cmrsp05, cmrsp08, cmrsp09, cmrsp12, cmrsp13, cmrsp16, cmrsp20)

# omits missing values (used for reliability and EFA)
cmrs10_old_shrunk <- na.omit(cmrs10_old_items)
```

```{r}
## Combine into 1 data frame

## demos, items, scores totals
cmrs_combo <- rbind(cmrs_young, cmrs_old)

### Add a column to dictate young and old groups
cmrs_combo$AgeGroup <- ifelse(cmrs_combo$child_age_main<12, "Younger", "Older")

## 21 items only
cmrs21_combo <- rbind(cmrs21_young_items, cmrs21_old_items)

## 21 shrunk items only (used for reliability and EFA)
cmrs21_shrunk_combo <- rbind(cmrs21_young_shrunk, cmrs21_old_shrunk)

## 10 items only
cmrs10_combo <- rbind(cmrs10_young_items, cmrs10_old_items)

## 10 items shrunk only (used for reliability and EFA)
cmrs10_shrunk_combo <- rbind(cmrs10_young_shrunk, cmrs10_old_shrunk)
```

#===================================================================
# CMRS 21
## Determine # of factors

```{r}
cortest.bartlett(cmrs21_shrunk_combo)
## statistically significant, p=0

KMO(cmrs21_shrunk_combo)
## .95 is "marvelous"
```


### Polychoric Screes (treats like lavaan)


```{r eigen scree nfactors}
## METHOD 1: Eigenvalue (Kaiser criterion) (ChatGPT code)- psych & nFactors

library(nFactors)

## polychoric correlation matrix
cmrs21_polychor_cor <- psych::polychoric(cmrs21_shrunk_combo)$rho


ev <- eigen(cmrs21_polychor_cor)$values
ap <- nFactors::parallel(subject = nrow(cmrs21_shrunk_combo),
                         var = ncol(cmrs21_shrunk_combo),
                         rep = 100,
                         cent = .95)
ns <- nFactors::nScree(x = ev, aparallel = ap$eigen$qevpea)

ns$Components # shows suggested # factors by rules
nFactors::plotnScree(ns)

## Findings: 3 factors above ev = 1
```

```{r parallel analysis scree}
## METHOD 2: parallel analysis- psych package only

psych::fa.parallel(
  cmrs21_shrunk_combo,
  fa  = "fa",
  fm  = "minres",
  cor = "poly"
)

##Suggests 6 factors
```
### Method Agreement

```{r}
library(parameters)

methods_21 <- n_factors(x = cmrs21_shrunk_combo,
                        type = "fa",
                        rotation = "promax",  ## for VSS
                        algorithm = "minres",
                        package = c("nFactors", "psych"),
                        correlation_matrix = psych::polychoric(cmrs21_shrunk_combo)$rho)
methods_21    ## print

as.data.frame(methods_21)
```


## EFA - CMRS 21

EFA asks: “What structure seems to be in the data?” 
      fit indices are less important. focus on factor loadings >.40)
      fit indices are helpful to compare differences in models
CFA asks: “Does this prespecified structure fit?”
ESEM asks: “Does that general structure fit better when cross-loadings are allowed?”
SEM asks: “Given an acceptable measurement model, how do the latent factors relate to other variables?”
  (after choosing the measurement model you trust most if you want to examine structural relations with diagnoses, impairment, demographics, etc.)

### 4 factors- Psych, Poly

```{r}
# 4 factor solution

library(psych)

set.seed(1234)
cmrs21_4poly_efa <- fa(
  cmrs21_shrunk_combo,
  cor = "poly",
  nfactors = 4,
  rotate = "promax",
  fm = "minres")  ## minres is default

print(cmrs21_4poly_efa, digits = 2, sort = TRUE, cut = .30)

cmrs21_4poly_efa$loadings

cmrs21_4poly_efa$residual[1:10]

fa.diagram(cmrs21_4poly_efa)

## Findings: 5 variables have double loadings.
## Factor 3 only has 3 items. Cum var: 67%
## RMSEA = .102 ; TLI = .878 ; RMSR = .03 ; MIC = 1.7 ; BIC = 2175.04
```


### EFA in Lavaan

```{r Range 1-6 factors, eval=FALSE, include=FALSE}
## Same estimator as ESEM. This is to support continuity. Testing 1,2,3,4,5,6 factors
library(lavaan)

var.names <- paste0("cmrsp", sprintf("%02d", 1:21))
set.seed(1234)
fit.efa <- efa(data = cmrs21_shrunk_combo, nfactors = 1:6, estimator = "WLSMV", ordered = var.names)
summary(fit.efa)
```


#### 3 Factors only

```{r unrotated (don't use), eval=FALSE, include=FALSE}
## same estimator as CFA. use over psych poly
var.names <- paste0("cmrsp", sprintf("%02d", 1:21))

set.seed(1234)
fit_3_un <- efa(data = cmrs21_shrunk_combo,
             nfactors = 3,
             estimator = "WLSMV",
             ordered = var.names)

summary(fit_3_un)
fitMeasures(fit_3_un, fit.measures = c("chisq.scaled", "df.scaled", "pvalue.scaled", 
                                    "rmsea.robust", "rmsea.scaled", "cfi.robust", 
                                    "cfi.scaled", "tli.robust", "tli.scaled", "srmr"))
fit_3_un$loadings
# Rotation affects factor loadings, not global model fit.
# Use unrotated solution for robust fit indices and rotated solution for interpretation.


## unrotated
# chisq.scaled                     853.154
# df.scaled                        150.000
# pvalue.scaled                      0.000
# rmsea.robust                       0.100
# cfi.robust                         0.917
# tli.robust                         0.884
# srmr                               0.035
```


```{r}
## same estimator as CFA. use over psych poly
var.names <- paste0("cmrsp", sprintf("%02d", 1:21))

set.seed(1234)
fit_3 <- efa(data = cmrs21_shrunk_combo,
             nfactors = 3,
             estimator = "WLSMV",
             ordered = var.names,
             rotation = "promax")

summary(fit_3)
fitMeasures(fit_3, fit.measures = c("chisq.scaled", "df.scaled", "pvalue.scaled",
                                    "rmsea.scaled", "cfi.scaled", "tli.scaled", "srmr",
                                    "rmsea.robust", "cfi.robust", "tli.robust"))
fit_3$loadings
# Rotation affects factor loadings, not global model fit.
# Use unrotated solution for robust fit indices and rotated solution for interpretation.


##rotated promax

# chisq.scaled  853.154
# df.scaled     150.000
# pvalue.scaled   0.000
# rmsea.scaled    0.046
# cfi.scaled      0.979
# tli.scaled      0.971
# srmr            0.035
# rmsea.robust       NA
# cfi.robust         NA
# tli.robust         NA


## unrotated
# chisq.scaled                     853.154
# df.scaled                        150.000
# pvalue.scaled                      0.000
# rmsea.robust                       0.100
# cfi.robust                         0.917
# tli.robust                         0.884
# srmr                               0.035
```

#### 4 Factors only

```{r}
## same estimator as CFA. use over psych poly
var.names <- paste0("cmrsp", sprintf("%02d", 1:21))

set.seed(1234)
fit_4 <- efa(data = cmrs21_shrunk_combo,
             nfactors = 4,
             estimator = "WLSMV",
             ordered = var.names,
             rotation = "promax")

summary(fit_4)
fitMeasures(fit_4, fit.measures = c("chisq.scaled", "df.scaled", "pvalue.scaled",
                                    "rmsea.scaled", "cfi.scaled", "tli.scaled", "srmr",
                                    "rmsea.robust", "cfi.robust", "tli.robust"))
fit_4$loadings


## rotated
# chisq.scaled  540.756
# df.scaled     132.000
# pvalue.scaled   0.000
# rmsea.scaled    0.037
# cfi.scaled      0.988
# tli.scaled      0.981
# srmr            0.027
# rmsea.robust       NA
# cfi.robust         NA
# tli.robust         NA


## unrotated
# chisq.scaled                     540.756
# df.scaled                        132.000
# pvalue.scaled                      0.000
# rmsea.robust                       0.089
# cfi.robust                         0.942
# tli.robust                         0.907
# srmr                               0.027

```


#### 5 Factors only
```{r}
var.names <- paste0("cmrsp", sprintf("%02d", 1:21))

set.seed(1234)
fit_5 <- efa(data = cmrs21_shrunk_combo,
             nfactors = 5,
             estimator = "WLSMV",
             ordered = var.names,
             rotation = "promax")

summary(fit_5)
fitMeasures(fit_5, fit.measures = c("chisq.scaled", "df.scaled", "pvalue.scaled",
                                    "rmsea.scaled", "cfi.scaled", "tli.scaled", "srmr",
                                    "rmsea.robust", "cfi.robust", "tli.robust"))
fit_5$loadings


### Factor 3 only has 2 items.
## rotated
# chisq.scaled  309.440
# df.scaled     115.000
# pvalue.scaled   0.000
# rmsea.scaled    0.028
# cfi.scaled      0.994
# tli.scaled      0.989
# srmr            0.020
# rmsea.robust       NA
# cfi.robust         NA
# tli.robust         NA


## unrotated
# chisq.scaled  309.440
# df.scaled     115.000
# pvalue.scaled   0.000
# rmsea.robust    0.077
# cfi.robust      0.962
# tli.robust      0.931
# srmr            0.020

```

#### 6 Factors only
```{r}
var.names <- paste0("cmrsp", sprintf("%02d", 1:21))

set.seed(1234)
fit_6 <- efa(data = cmrs21_shrunk_combo,
             nfactors = 6,
             estimator = "WLSMV",
             ordered = var.names,
             rotation = "promax")

summary(fit_6)
fitMeasures(fit_6, fit.measures = c("chisq.scaled", "df.scaled", "pvalue.scaled",
                                    "rmsea.scaled", "cfi.scaled", "tli.scaled", "srmr",
                                    "rmsea.robust", "cfi.robust", "tli.robust"))
fit_6$loadings

## rotated
# chisq.scaled  219.362
# df.scaled      99.000
# pvalue.scaled   0.000
# rmsea.scaled    0.023
# cfi.scaled      0.996
# tli.scaled      0.992
# srmr            0.015
# rmsea.robust       NA
# cfi.robust         NA
# tli.robust         NA


## unrotated
# chisq.scaled  219.362
# df.scaled      99.000
# pvalue.scaled   0.000
# rmsea.robust    0.061
# cfi.robust      0.979
# tli.robust      0.956
# srmr            0.015
```

## ABACAB CFA
no rotation added, since ABACAB model is rotated

### 4 Factor - psych
```{r}
#CFA using 4 factor model based on ABACAB Scree Plot (poly, promax, psych package)

set.seed(1234)

# Specify factor structure
cfa_abacab_4_21_psych.model<- '
ADHD =~ cmrsp06 + cmrsp07 + cmrsp08 + cmrsp09 + cmrsp10 + cmrsp11
Psychosis =~ cmrsp13 + cmrsp19 + cmrsp20 + cmrsp21
Irritability =~ cmrsp02 + cmrsp16 + cmrsp18
Mania =~ cmrsp01 + cmrsp03 + cmrsp04 + cmrsp05 + cmrsp12 + cmrsp14 + cmrsp15 + cmrsp17
'

# Fit CFA
fit_cfa_abacab_4_21_psych<- cfa(cfa_abacab_4_21_psych.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"))

# Display CFA result
summary(fit_cfa_abacab_4_21_psych, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED
## Estimator: WLSMV. Chi squared = 1476.796 ; df = 183 ; RMSEA = .056 ; CFI = .962, TLI = .956 ; SRMSR = .056
```


```{r}
factor_cols <- c("ADHD", "Psychosis", "Irritability", "Mania")

# Get standardized parameter estimates from the CFA model
std_loading_wide <- parameterEstimates(fit_cfa_abacab_4_21_psych, standardized = TRUE) %>%
  
  # Keep only factor loadings
  dplyr::filter(op == "=~") %>%
  
  # Keep factor name, item name, and standardized loading
  dplyr::select(Factor = lhs, Item = rhs, Std_Loading = std.all) %>%
  
  # Reshape so each item is a row and each factor is a column
  tidyr::pivot_wider(names_from = Factor, values_from = Std_Loading)

# For each item, find the factor with the largest absolute loading
std_loading_wide %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    
    # Name of factor with strongest loading
    strongest_factor = names(c_across(all_of(factor_cols)))[which.max(abs(c_across(all_of(factor_cols))))],
    
    # Size of strongest loading
    strongest_loading = max(abs(c_across(all_of(factor_cols))), na.rm = TRUE)
  ) %>%
  dplyr::ungroup() %>% # Remove rowwise grouping and return to a regular data frame/tibble
  dplyr::mutate(across(where(is.numeric), ~ round(.x, 3)))  # round to 3 decimals
```


#### 4 factor- lavaan

```{r}
#CFA using 4 factor model based on ABACAB Scree Plot (lavaan)

set.seed(1234)

# Specify factor structure
cfa_abacab_4_21_lav.model<- '
F1 =~ cmrsp01 + cmrsp03 + cmrsp04 + cmrsp05 + cmrsp12 + cmrsp14 + cmrsp15 + cmrsp17
F2 =~ cmrsp06 + cmrsp07 + cmrsp08 + cmrsp09 + cmrsp10 + cmrsp11
F3 =~ cmrsp02 + cmrsp16 + cmrsp18
F4 =~ cmrsp13 + cmrsp19 + cmrsp20 + cmrsp21
'

# Fit CFA
fit_cfa_abacab_4_21_lav <- cfa(cfa_abacab_4_21_lav.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"))

# Display CFA result
summary(fit_cfa_abacab_4_21_lav, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED
## Estimator: WLSMV. Chi squared = 1368.449 ; df = 183 ; RMSEA = .054 ; CFI = .965, TLI = .960 ; SRMR = .053
```



### 5 Factor
```{r}
#CFA using ABACAB 5 factor poly model

set.seed(1234)

# Specify factor structure
cfa_abacab_5_21.model<- '
ADHD =~ cmrsp06 + cmrsp07 + cmrsp08 + cmrsp09 + cmrsp10 + cmrsp11
Psychosis =~ cmrsp20 + cmrsp21 + cmrsp19
Irritability =~ cmrsp02 + cmrsp16 + cmrsp18
Maniapt1 =~ cmrsp01 + cmrsp03 + cmrsp04 + cmrsp05 + cmrsp12 + cmrsp17
Maniapt2 =~ cmrsp13 + cmrsp14 + cmrsp15
'

# Fit CFA
fit_cfa_abacab_5_21<- cfa(cfa_abacab_5_21.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"))

# Display CFA result
summary(fit_cfa_abacab_5_21, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED
## Estimator: WLSMV. Chi squared = 1370.030 ; df = 179 ; RMSEA = .055 ; CFI = .965, TLI = .959 ; SRMSR = .052
```

## ESEM


#### 3 factor rotated
```{r 3 Factor unrotated, eval=FALSE, include=FALSE}
library(lavaan)

set.seed(1234)
esem3.model <- '
    efa("efa")*f1 +
    efa("efa")*f2 +
    efa("efa")*f3 =~ cmrsp01 + cmrsp02 + cmrsp04 + cmrsp05 + cmrsp08 + cmrsp09 +
    cmrsp12 + cmrsp13 + cmrsp16 + cmrsp20 + cmrsp03 + cmrsp06 +
    cmrsp07 + cmrsp10 + cmrsp11 + cmrsp14 + cmrsp15 + cmrsp17 +
    cmrsp18 + cmrsp19 + cmrsp21
'
fit.esem3 <- sem(model = esem3.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"))

summary(fit.esem3, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED (ignore robust)
## Estimator: WLSMV. Chi squared = 803.396 ; df = 150 ; RMSEA = .046 ; CFI = .979, TLI = .971 ; SRMR = .035

# F1: 06, 07, 08, 09
# F2: 01, 03, 04, 05, 10, 12, 13, 14, 15, 17, 19, 20, 21
# F3: 02, 11, 16, 18

## Cross Loadings:
# cmrsp10: F2 (.517) vs F1 (.461)
# cmrsp19: F2 (.507) vs F3 (.392)
# cmrsp08: F1 (.436) vs F3 (.347)
# cmrsp11: F3 (.503) vs F1 (.405)
```

```{r}
library(lavaan)

set.seed(1234)
esem3.model <- '
    efa("efa")*f1 +
    efa("efa")*f2 +
    efa("efa")*f3 =~ cmrsp01 + cmrsp02 + cmrsp04 + cmrsp05 + cmrsp08 + cmrsp09 +
    cmrsp12 + cmrsp13 + cmrsp16 + cmrsp20 + cmrsp03 + cmrsp06 +
    cmrsp07 + cmrsp10 + cmrsp11 + cmrsp14 + cmrsp15 + cmrsp17 +
    cmrsp18 + cmrsp19 + cmrsp21
'
fit.esem3.rot <- sem(model = esem3.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"), rotation = "promax")

summary(fit.esem3.rot, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED (ignore robust)
## Estimator: WLSMV. Chi squared = 803.396 ; df = 150 ; RMSEA = .046 ; CFI = .979, TLI = .971 ; SRMR = .035

# F1: 02, 16, 18
# F2: 03, 04, 05, 13, 14, 15, 19, 20, 21
# F3: 01, 06, 07, 08, 09, 10, 11, 12, 17
```

```{r}
# Get standardized parameter estimates from the ESEM model
std_loading_wide <- parameterEstimates(fit.esem3.rot, standardized = TRUE) %>%

  # Keep only factor loadings
  dplyr::filter(op == "=~") %>%

  # Keep factor name, item name, and standardized loading
  dplyr::select(Factor = lhs, Item = rhs, Std_Loading = std.all) %>%

  # Reshape so each item is a row and each factor is a column
  tidyr::pivot_wider(names_from = Factor, values_from = Std_Loading)

# For each item, find the factor with the largest absolute loading
std_loading_wide %>%
  dplyr::rowwise() %>%
  dplyr::mutate(

    # Name of factor with strongest loading
    strongest_factor = names(c_across(starts_with("f")))[which.max(abs(c_across(starts_with("f"))))],

    # Size of strongest loading
    strongest_loading = max(abs(c_across(starts_with("f"))), na.rm = TRUE)
  ) %>%
  dplyr::ungroup() %>% # Remove rowwise grouping and return to a regular data frame/tibble
  dplyr::mutate(across(where(is.numeric), ~ round(.x, 3)))  # round to 3 decimals
```


#### 4 factor rotated

```{r 4 Factor unrotated, eval=FALSE, include=FALSE}
library(lavaan)

set.seed(1234)
esem4.model <- '
    efa("efa")*f1 +
    efa("efa")*f2 +
    efa("efa")*f3 +
    efa("efa")*f4 =~ cmrsp01 + cmrsp02 + cmrsp04 + cmrsp05 + cmrsp08 + cmrsp09 +
    cmrsp12 + cmrsp13 + cmrsp16 + cmrsp20 + cmrsp03 + cmrsp06 +
    cmrsp07 + cmrsp10 + cmrsp11 + cmrsp14 + cmrsp15 + cmrsp17 +
    cmrsp18 + cmrsp19 + cmrsp21
'
fit.esem4 <- sem(model = esem4.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"))

summary(fit.esem4, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED (ignore robust)
## Estimator: WLSMV. Chi squared = 507.598 ; df = 132 ; RMSEA = .038 ; CFI = .988, TLI = .980 ; SRMSR = .027

# F1: 06, 07, 10
# F3: 02, 08, 09, 11, 16, 18
# F4: 01, 03, 04, 05, 12, 13, 14, 15, 17, 19, 20, 21
# F2: no primary items

## Cross Loadings:
# cmrsp10: F1 (.539) and F4 (.515)
# cmrsp09: F3 (.454) and F1 (.414)
# cmrsp12: F4 (.459) and F2 (.376)
# cmrsp08: F3 (.578) and F2 (.375)
# cmrsp19: F4 (.525) and F3 (.350)
# cmrsp01: F4 (.437) and F2 (.304)
```

```{r}
library(lavaan)

set.seed(1234)
esem4.model <- '
    efa("efa")*f1 +
    efa("efa")*f2 +
    efa("efa")*f3 +
    efa("efa")*f4 =~ cmrsp01 + cmrsp02 + cmrsp04 + cmrsp05 + cmrsp08 + cmrsp09 +
    cmrsp12 + cmrsp13 + cmrsp16 + cmrsp20 + cmrsp03 + cmrsp06 +
    cmrsp07 + cmrsp10 + cmrsp11 + cmrsp14 + cmrsp15 + cmrsp17 +
    cmrsp18 + cmrsp19 + cmrsp21
'
fit.esem4.rot <- sem(model = esem4.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"), rotation = "promax")

summary(fit.esem4.rot, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED (ignore robust)
## Estimator: WLSMV. Chi squared = 540.756 ; df = 132 ; RMSEA = .037 ; CFI = .988, TLI = .981 ; SRMR = .027

# F1: 02, 16, 18
# F2: 01, 05, 08, 12
# F3: 03, 04, 13, 14, 15, 17, 19, 20, 21
# F4: 06, 07, 09, 10, 11
```

```{r}
# Get standardized parameter estimates from the ESEM model
std_loading_wide <- parameterEstimates(fit.esem4.rot, standardized = TRUE) %>%

  # Keep only factor loadings
  dplyr::filter(op == "=~") %>%

  # Keep factor name, item name, and standardized loading
  dplyr::select(Factor = lhs, Item = rhs, Std_Loading = std.all) %>%

  # Reshape so each item is a row and each factor is a column
  tidyr::pivot_wider(names_from = Factor, values_from = Std_Loading)

# For each item, find the factor with the largest absolute loading
std_loading_wide %>%
  dplyr::rowwise() %>%
  dplyr::mutate(

    # Name of factor with strongest loading
    strongest_factor = names(c_across(starts_with("f")))[which.max(abs(c_across(starts_with("f"))))],

    # Size of strongest loading
    strongest_loading = max(abs(c_across(starts_with("f"))), na.rm = TRUE)
  ) %>%
  dplyr::ungroup() %>% # Remove rowwise grouping and return to a regular data frame/tibble
  dplyr::mutate(across(where(is.numeric), ~ round(.x, 3)))  # round to 3 decimals
```


```{r}
## modification

modindices(fit.esem4.rot, minimum.value = 10, sort = T)
```

```{r}
## Factor correlations

lavInspect(fit.esem4.rot, "cor.lv")

# f1 with f2 = .322
# f1 with f3 = .417
# f1 with f4 = .358
# f2 with f3 = .104
# f2 with f4 = .241
# f3 with f4 = .746
```


```{r}
## plot model

semPlot::semPaths(fit.esem4.rot, "std")
```


#### 5 factor rotated

```{r 5 Factor unrotated, eval=FALSE, include=FALSE}
library(lavaan)

set.seed(1234)
esem5.model <- '
    efa("efa")*f1 +
    efa("efa")*f2 +
    efa("efa")*f3 +
    efa("efa")*f4 +
    efa("efa")*f5 =~ cmrsp01 + cmrsp02 + cmrsp04 + cmrsp05 + cmrsp08 + cmrsp09 +
    cmrsp12 + cmrsp13 + cmrsp16 + cmrsp20 + cmrsp03 + cmrsp06 +
    cmrsp07 + cmrsp10 + cmrsp11 + cmrsp14 + cmrsp15 + cmrsp17 +
    cmrsp18 + cmrsp19 + cmrsp21
'
fit.esem5 <- sem(model = esem5.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"))

summary(fit.esem5, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED (ignore robust)
## Estimator: WLSMV. Chi squared = 291.971 ; df = 115 ; RMSEA = .028 ; CFI = .994, TLI = .989 ; SRMR = .020

# F1 = 01, 03, 06, 07, 10
# F2 = 08, 09, 11
# F3 = 05, 12
# F4 = 02, 16, 18
# F5 = 04, 13, 14, 15, 17, 19, 20, 21

## Cross loadings:
# cmrsp07: F1 (.594), also F2 (.494)
# cmrsp08: F2 (.524), also F3 (.487)
# cmrsp09: F2 (.597), also F3 (.400)
# cmrsp12: F3 (.409), also F1 (.394)
# cmrsp03: F1 (.502), also F5 (.337)
# cmrsp04: F5 (.570), also F3 (.376)
# cmrsp16: F4 (.709), also F5 (.310)
```

```{r}
library(lavaan)

set.seed(1234)
esem5.model <- '
    efa("efa")*f1 +
    efa("efa")*f2 +
    efa("efa")*f3 +
    efa("efa")*f4 +
    efa("efa")*f5 =~ cmrsp01 + cmrsp02 + cmrsp04 + cmrsp05 + cmrsp08 + cmrsp09 +
    cmrsp12 + cmrsp13 + cmrsp16 + cmrsp20 + cmrsp03 + cmrsp06 +
    cmrsp07 + cmrsp10 + cmrsp11 + cmrsp14 + cmrsp15 + cmrsp17 +
    cmrsp18 + cmrsp19 + cmrsp21
'
fit.esem5.rot <- sem(model = esem5.model, data = cmrs21_shrunk_combo, estimator = "WLSMV",
                  ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05",
            "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10",
            "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15",
            "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21"), rotation = "promax")

summary(fit.esem5.rot, fit.measures = TRUE, standardized = TRUE)

## Findings: focus on SCALED (ignore robust)
## Estimator: WLSMV. Chi squared = 309.440 ; df = 115 ; RMSEA = .028 ; CFI = .994, TLI = .989 ; SRMR = .020

# F1 = 01, 03, 06, 07, 10
# F2 = 08, 09, 11
# F3 = 05, 12
# F4 = 02, 16, 18
# F5 = 04, 13, 14, 15, 17, 19, 20, 21

## Cross loadings:
# cmrsp07: F1 (.594), also F2 (.494)
# cmrsp08: F2 (.524), also F3 (.487)
# cmrsp09: F2 (.597), also F3 (.400)
# cmrsp12: F3 (.409), also F1 (.394)
# cmrsp03: F1 (.502), also F5 (.337)
# cmrsp04: F5 (.570), also F3 (.376)
# cmrsp16: F4 (.709), also F5 (.310)
```


```{r}
## No modifications

modindices(fit.esem5, minimum.value = 10, sort = T)
```

```{r}
## Factor correlations

lavInspect(fit.esem5, "cor.lv")

```

```{r}
# Get standardized parameter estimates from the ESEM model
std_loading_wide <- parameterEstimates(fit.esem5, standardized = TRUE) %>%

  # Keep only factor loadings
  dplyr::filter(op == "=~") %>%

  # Keep factor name, item name, and standardized loading
  dplyr::select(Factor = lhs, Item = rhs, Std_Loading = std.all) %>%

  # Reshape so each item is a row and each factor is a column
  tidyr::pivot_wider(names_from = Factor, values_from = Std_Loading)

# For each item, find the factor with the largest absolute loading
std_loading_wide %>%
  dplyr::rowwise() %>%
  dplyr::mutate(

    # Name of factor with strongest loading
    strongest_factor = names(c_across(starts_with("f")))[which.max(abs(c_across(starts_with("f"))))],

    # Size of strongest loading
    strongest_loading = max(abs(c_across(starts_with("f"))), na.rm = TRUE)
  ) %>%
  dplyr::ungroup() %>% # Remove rowwise grouping and return to a regular data frame/tibble
  dplyr::mutate(across(where(is.numeric), ~ round(.x, 3)))  # round to 3 decimals
```

<!-- #### 6 Factor- poor -->

<!-- ```{r} -->
<!-- library(lavaan) -->

<!-- set.seed(1234) -->
<!-- esem6.model <- ' -->
<!--     efa("efa")*f1 +  -->
<!--     efa("efa")*f2 +  -->
<!--     efa("efa")*f3 + -->
<!--     efa("efa")*f4 + -->
<!--     efa("efa")*f5 + -->
<!--     efa("efa")*f6 =~ cmrsp06 + cmrsp07 + cmrsp08 + cmrsp09 + cmrsp10 + cmrsp11 + -->
<!--     cmrsp19 + cmrsp20 + cmrsp21 + cmrsp02 + cmrsp16 + cmrsp18 +cmrsp01 + cmrsp03 + -->
<!--     cmrsp04 + cmrsp05 + cmrsp12 + cmrsp14 + cmrsp15 + cmrsp17 + cmrsp13 -->
<!-- ' -->
<!-- fit.esem6 <- sem(model = esem6.model, data = cmrs21_shrunk_combo, estimator = "WLSMV", -->
<!--                   ordered = c("cmrsp01","cmrsp02","cmrsp03","cmrsp04","cmrsp05", -->
<!--             "cmrsp06","cmrsp07","cmrsp08","cmrsp09","cmrsp10", -->
<!--             "cmrsp11","cmrsp12","cmrsp13","cmrsp14","cmrsp15", -->
<!--             "cmrsp16","cmrsp17","cmrsp18","cmrsp19","cmrsp20","cmrsp21")) -->

<!-- summary(fit.esem6, fit.measures = TRUE, standardized = TRUE) -->

<!-- ## Findings: focus on SCALED (ignore robust) -->
<!-- ## Estimator: WLSMV. Chi squared = 219.260 ; df = 99 ; RMSEA = .025 ; CFI = .996, TLI = .992 ; SRMSR = .016 -->

<!-- # F1: 06, 07, 10, 03 -->
<!-- # F2: 09, 11 -->
<!-- # F3: 01, 08, 05, 12 -->
<!-- # F4: 17 -->
<!-- # F5: 02, 16, 18 -->
<!-- # F6: 04, 13, 14, 15, 19, 20, 21 -->
<!-- #  -->
<!-- # # Cross loadings: -->
<!-- # cmrsp01: F3 (.393) vs F1 (.386) — basically tied -->
<!-- # cmrsp11: F2 (.409), also F4 (.340) and F5 (.301) -->
<!-- # cmrsp17: F4 (.298), but this is weak overall -->
<!-- # cmrsp05: F3 (.373), also F6 (.275) -->
<!-- # cmrsp15: F6 (.441), also F4 (.409) -->
<!-- # cmrsp07: F1 (.654), also F2 (.456) -->
<!-- ``` -->

<!-- #=================================================================== -->
<!-- # CMRS 10 -->

<!-- ## Determine # of factors -->

<!-- ```{r} -->
<!-- psych::fa.parallel( -->
<!--   cmrs10_shrunk_combo, -->
<!--   fa  = "fa", -->
<!--   fm  = "minres", -->
<!--   cor = "poly" -->
<!-- ) -->
<!-- ``` -->

<!-- ## EFA - CMRS 10 -->

<!-- EFA asks: “What structure seems to be in the data?”  -->
<!-- CFA asks: “Does this prespecified structure fit?” -->
<!-- ESEM asks: “Does that general structure fit better when cross-loadings are allowed?” -->
<!-- SEM asks: “Given an acceptable measurement model, how do the latent factors relate to other variables?” -->
<!--   (after choosing the measurement model you trust most if you want to examine structural relations with diagnoses, impairment, demographics, etc.) -->


<!-- ### 4 factors- Psych, Pearson -->

<!-- ```{r} -->
<!-- # 4 factor solution, Pearson's r -->

<!-- library(psych) -->

<!-- set.seed(1234) -->
<!-- cmrs10_4factor_r_efa <- fa( -->
<!--   cmrs10_shrunk_combo, -->
<!--   nfactors = 4, -->
<!--   rotate = "promax", -->
<!--   fm = "minres")  ## minres is default -->

<!-- print(cmrs10_4factor_r_efa, digits = 2, sort = TRUE, cut = .30) -->

<!-- cmrs10_4factor_r_efa$loadings -->

<!-- cmrs10_4factor_r_efa$residual[1:10] -->

<!-- fa.diagram(cmrs10_4factor_r_efa) -->

<!-- ## Findings: factor 4 has one item -->
<!-- ## RMSEA = .054 ; TLI = .935 ; RMSR = .03 ; MIC = 1.6 ; BIC = -24.58 -->
<!-- ``` -->

<!-- ### 4 factors 10 item- Psych, Poly -->

<!-- ```{r} -->
<!-- # 4 factor solution -->

<!-- library(psych) -->

<!-- set.seed(1234) -->
<!-- cmrs10_4poly_efa <- fa( -->
<!--   cmrs10_shrunk_combo, -->
<!--   cor = "poly", -->
<!--   nfactors = 4, -->
<!--   rotate = "promax", -->
<!--   fm = "minres")  ## minres is default -->

<!-- print(cmrs10_4poly_efa, digits = 2, sort = TRUE, cut = .30) -->

<!-- cmrs10_4poly_efa$loadings -->

<!-- cmrs10_4poly_efa$residual[1:10] -->

<!-- fa.diagram(cmrs10_4poly_efa) -->

<!-- ## Findings: 2 variables have double loadings. item 4 is equal. -->
<!-- ## Factor 3 only has 1 item. Cum var: 70% -->
<!-- ## RMSEA = .074 ; TLI = .959 ; RMSR = .03 ; MIC = 1.3 ; BIC = 62.6 -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ##This is to support continuity. Testing 1,2,3,4 factors -->
<!-- library(lavaan) -->

<!-- set.seed(1234) -->
<!-- fit10.efa <- efa(data = cmrs10_shrunk_combo, nfactors = 1:3,  -->
<!--                estimator = "WLSMV", ordered =names(cmrs10_shrunk_combo)) -->
<!-- summary(fit10.efa) -->
<!-- ``` -->

<!-- ### 3 factors 10 item- Psych, Poly -->

<!-- ```{r} -->
<!-- # 4 factor solution -->

<!-- library(psych) -->

<!-- set.seed(1234) -->
<!-- cmrs10_3poly_efa <- fa( -->
<!--   cmrs10_shrunk_combo, -->
<!--   cor = "poly", -->
<!--   nfactors = 3, -->
<!--   rotate = "promax", -->
<!--   fm = "minres")  ## minres is default -->

<!-- print(cmrs10_3poly_efa, digits = 2, sort = TRUE, cut = .30) -->

<!-- cmrs10_3poly_efa$loadings -->

<!-- cmrs10_3poly_efa$residual[1:10] -->

<!-- fa.diagram(cmrs10_3poly_efa) -->

<!-- ## Findings: 2 variables have double loadings. item 4 is equal. -->
<!-- ## Factor 3 only has 1 item. Cum var: 70% -->
<!-- ## RMSEA = .098 ; TLI = .929 ; RMSR = .02 ; MIC = 1.3 ; BIC = 266.51 -->
<!-- ``` -->


<!-- ### Lavaan -->

<!-- #### 3 Factors -->
<!-- ```{r} -->
<!-- ## same estimator as CFA. use over psych poly -->

<!-- set.seed(1234) -->
<!-- fit10_3 <- efa(data = cmrs10_shrunk_combo, -->
<!--              nfactors = 3, -->
<!--              estimator = "WLSMV", -->
<!--              ordered = c("cmrsp01","cmrsp02","cmrsp04","cmrsp05", -->
<!--             "cmrsp08","cmrsp09","cmrsp12","cmrsp13","cmrsp16","cmrsp20")) -->

<!-- summary(fit10_3, fit.measures = TRUE, standardized = TRUE) -->

<!-- fit10_3$loadings -->

<!-- ##  -->

<!-- # Fit measures: -->
<!-- #                   chisq   df   pvalue    cfi    rmsea -->
<!-- #   nfactors = 3   75.174   18      0     0.977    0.089 -->
<!-- ``` -->

<!-- #### 4 Factors - doesn't run -->
<!-- ```{r} -->
<!-- ## same estimator as CFA. WILL NOT RUN -->

<!-- set.seed(1234) -->
<!-- fit10_4 <- efa(data = cmrs10_shrunk_combo, -->
<!--              nfactors = 4, -->
<!--              estimator = "WLSMV", -->
<!--              ordered = c("cmrsp01","cmrsp02","cmrsp04","cmrsp05", -->
<!--             "cmrsp08","cmrsp09","cmrsp12","cmrsp13","cmrsp16","cmrsp20")) -->

<!-- summary(fit10_4, fit.measures = TRUE, standardized = TRUE) -->

<!-- fit10_4$loadings -->

<!-- ## WILL NOT RUN -->

<!-- # Fit measures: -->
<!-- #                   chisq   df   pvalue    cfi    rmsea -->
<!-- #   nfactors = 4 -->
<!-- ``` -->


<!-- ### ABACAB CFA -->

<!-- #### 4 Factor - USE FOR PAPER -->
<!-- ```{r} -->
<!-- #CFA using 4 factor model based on ABACAB Scree Plot (poly) -->

<!-- set.seed(1234) -->

<!-- # Specify factor structure -->
<!-- cfa_abacab_4_10.model<- ' -->
<!-- Factor1 =~ cmrsp08 + cmrsp09 -->
<!-- Factor2 =~ cmrsp02 + cmrsp16 -->
<!-- Factor3 =~ cmrsp04 + cmrsp20 + cmrsp05 + cmrsp13 -->
<!-- Factor4 =~ cmrsp01 + cmrsp12 -->
<!-- ' -->

<!-- # Fit CFA -->
<!-- fit_cfa_abacab_4_10<- cfa(cfa_abacab_4_10.model, data = cmrs10_shrunk_combo, estimator = "WLSMV", -->
<!--                   ordered = names(cmrs10_shrunk_combo)) -->

<!-- # Display CFA result -->
<!-- summary(fit_cfa_abacab_4_10, fit.measures = TRUE, standardized = TRUE) -->

<!-- ## Findings: focus on SCALED -->
<!-- ## Estimator: WLSMV. Chi squared = 191.171 ; df = 29 ; RMSEA = .050 ; CFI = .984, TLI = .975 ; SRMSR = .042 -->
<!-- ``` -->


<!-- ```{r} -->
<!-- # Get standardized parameter estimates from the CFA model -->
<!-- std_loading_wide <- parameterEstimates(fit_cfa_abacab_4_10, standardized = TRUE) %>% -->

<!--   # Keep only factor loadings -->
<!--   dplyr::filter(op == "=~") %>% -->

<!--   # Keep factor name, item name, and standardized loading -->
<!--   dplyr::select(Factor = lhs, Item = rhs, Std_Loading = std.all) %>% -->

<!--   # Reshape so each item is a row and each factor is a column -->
<!--   tidyr::pivot_wider(names_from = Factor, values_from = Std_Loading) -->

<!-- # For each item, find the factor with the largest absolute loading -->
<!-- std_loading_wide %>% -->
<!--   dplyr::rowwise() %>% -->
<!--   dplyr::mutate( -->

<!--     # Name of factor with strongest loading -->
<!--     strongest_factor = names(c_across(starts_with("f")))[which.max(abs(c_across(starts_with("f"))))], -->

<!--     # Size of strongest loading -->
<!--     strongest_loading = max(abs(c_across(starts_with("f"))), na.rm = TRUE) -->
<!--   ) %>% -->
<!--   dplyr::ungroup() %>% # Remove rowwise grouping and return to a regular data frame/tibble -->
<!--   dplyr::mutate(across(where(is.numeric), ~ round(.x, 3)))  # round to 3 decimals -->
<!-- ``` -->

<!-- #### Modifications -->
<!-- ```{r} -->
<!-- fit_cfa_mod_abacab_4_10 <- cfa(cfa_abacab_4_10.model, -->
<!--            data = cmrs10_shrunk_combo) -->
<!-- modindices(fit_cfa_mod_abacab_4_10, sort = TRUE, maximum.number = 10) -->
<!-- ``` -->

<!-- #### Composite Reliability -->
<!-- ```{r} -->
<!-- compRelSEM(fit_cfa_mod_abacab_4_10, tau.eq = FALSE, ord.scale = TRUE, return.total = TRUE) -->

<!-- ## values above 0.7 indicate acceptable internal consistency, while values above 0.8 suggest good reliability.  -->

<!-- ##https://medium.com/@luisdzanetta/confirmatory-factor-analysis-in-r-a-practical-guide-with-lavaan-35371cccd4f5 -->
<!-- ``` -->


<!-- <!-- ### ESEM - CMRS 10 --> -->


<!-- <!-- #### 3 Factor --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- library(lavaan) --> -->

<!-- <!-- set.seed(1234) --> -->
<!-- <!-- esem3_10.model <- ' --> -->
<!-- <!--     efa("efa")*f1 + --> -->
<!-- <!--     efa("efa")*f2 + --> -->
<!-- <!--     efa("efa")*f3 =~ cmrsp08 + cmrsp09 + cmrsp02 + cmrsp16 + cmrsp04 + cmrsp20  --> -->
<!-- <!--     + cmrsp05 + cmrsp13 + cmrsp01 + cmrsp12 --> -->
<!-- <!-- ' --> -->
<!-- <!-- fit.esem3_10 <- sem(model = esem3_10.model, data = cmrs10_shrunk_combo, estimator = "WLSMV", --> -->
<!-- <!--                   ordered = names(cmrs10_shrunk_combo)) --> -->

<!-- <!-- summary(fit.esem3_10, fit.measures = TRUE, standardized = TRUE) --> -->

<!-- <!-- lavInspect(fit.esem3_10, "std")$lambda ## loadings --> -->

<!-- <!-- ## Findings: focus on SCALED (ignore robust) --> -->
<!-- <!-- ## Estimator: WLSMV. Chi squared = 507.598 ; df = 132 ; RMSEA = .038 ; CFI = .988, TLI = .980 ; SRMSR = .027 --> -->
<!-- <!-- ``` --> -->


<!-- <!-- #### 4 Factor --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- library(lavaan) --> -->

<!-- <!-- set.seed(1234) --> -->
<!-- <!-- esem4_10.model <- ' --> -->
<!-- <!--     efa("efa")*f1 + --> -->
<!-- <!--     efa("efa")*f2 + --> -->
<!-- <!--     efa("efa")*f3 + --> -->
<!-- <!--     efa("efa")*f4 =~ cmrsp08 + cmrsp09 + cmrsp02 + cmrsp16 + cmrsp04 + cmrsp20  --> -->
<!-- <!--     + cmrsp05 + cmrsp13 + cmrsp01 + cmrsp12 --> -->
<!-- <!-- ' --> -->
<!-- <!-- fit.esem4_10 <- sem(model = esem4_10.model, data = cmrs10_shrunk_combo, estimator = "WLSMV", --> -->
<!-- <!--                   ordered = names(cmrs10_shrunk_combo)) --> -->

<!-- <!-- summary(fit.esem4_10, fit.measures = TRUE, standardized = TRUE) --> -->

<!-- <!-- ## Findings: focus on SCALED (ignore robust) --> -->
<!-- <!-- ## Estimator: WLSMV. Chi squared = 507.598 ; df = 132 ; RMSEA = .038 ; CFI = .988, TLI = .980 ; SRMSR = .027 --> -->
<!-- <!-- ``` --> -->


